Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-11 cordillera-cycle.tex
Add deglaciation profiles in manuscript.
Add deglaciation time-series in manuscript.

@@

>>>>

% fig:deglacseries
\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) \textbf{(top)}, and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent \textbf{(bottom)}.}
  \label{fig:deglacseries}
\end{figure}

@@

% fig:profiles
\begin{figure}
  \includegraphics{profiles}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,\unit{kyr}) in the GRIP 6\,\unit{km}
           simulation, corresponding to the four transects indicated in
           Fig.~\ref{fig:deglac}.}
  \label{fig:profiles}
\end{figure}
